Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold Standard Items

### 2025-06-18 analysis/primary_analyses.qmd
adjust labels for tbl-1

table1 <- dat_desc |>
  mutate(Geschlecht = factor(Geschlecht), 
    Bildung = factor(Bildung), 
    Muttersprache = factor(Muttersprache)) |>
  flextable::summarizor(by = "categories") |>
  flextable::as_flextable() |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table1
```

>>>>

table1 <- dat_desc |>
  rename(Gender = Geschlecht, Education = Bildung, `Mother tongue` = Muttersprache, Age = Alter_realW) |>
  mutate(Gender = factor(Gender, levels = 1:2, labels = c("women", "men")), 
    Education = factor(Education, levels = 1:6, labels = c("no school leaving certificate", "secondary school leaving certificate/elementary school or equivalent", "secondary school or equivalent", "vocational baccalaureate or high school diploma", "college degree or university degree", "doctorate or habilitation")), 
    `Mother tongue` = factor(`Mother tongue`, levels = 1:2, labels = c("German", "Other"))) |>
  flextable::summarizor(by = "categories") |>
  flextable::as_flextable() |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table1
```

### 2025-06-18 manuscript.qmd
adjust labels for tbl-1

```{r}
#| label: "tbl-1"
#| tbl-cap: Sample characteristics within the response category conditions
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: Percent = Percentage within the subsample.

>>>>

```{r}
#| label: "tbl-1"
#| tbl-cap: Sample characteristics within response category conditions
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: SD = standard deviation, IQR = interquartile range.
